% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{bibentry}
\usepackage{natbib}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Chenzhi Zhu}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Curriculum Vitae},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.4in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

% Make lists with bullets
\newenvironment{listed}{
  \begin{list}{$\cdot$}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lr}
      \textbf{#1} & #2 \\
      \textit{\normalsize #3} & \textit{\normalsize #4} \\
    \end{tabular*}\vspace{-5pt}
}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Add publications ref
\usepackage{hanging}
\newcommand\publication[1]{%
  \smallskip\par\hangpara{1.5em}{1}\bibentry{#1}\smallskip
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.55\linewidth}
  {Institute for Interdisciplinary Information Sciences, \\
    Tsinghua University, P.R. China}
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +8613263337088 \\
    Email: & \href{mailto:zhucz16@mails.tsinghua.edu.cn}{\tt zhucz16@mails.tsinghua.edu.cn}, \\
           & \href{mailto:mrbrtpt@gmail.com}{\tt mrbrtpt@gmail.com} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
    \resumeSubheading{Tsinghua University}{Beijing, China}{B.S. in Institute for Interdisciplinary Information Sciences}{2016-present}\\
    \begin{listed}
	    \item Overal GPA: \textbf{3.83/4.00}; Ranking: 6/38
        \item Selected awards: Yao Award; Freshman Scholarship
        \item Selected to Tsinghua Xuetang Special Pilot CS Class, directed by Prof. Andrew Yao.
        \item Admission given by \emph{Gold Medal} in the National Olympiad of Informatics 2015.
        \item Visiting student to Carnegie Mellon University
    \end{listed}
\end{itemize}

\section*{Research Experience}
\begin{itemize}
    \resumeSubheading{Carnegie Mellon University}{Pittsburgh, Pennsylvania}
    {Research Assistant with Professor Vipul Goyal}{Feb. 2019 – present}
    \resumeItemListStart
    \resumeItem{Efficient Multiparty Computation Protocol with Guaranteed Output Delivery}{
    \begin{listed}
        \item Explored past results on the communication complexity of MPC protocol with guaranteed output delivery.
   	    \item Proposed some ideas in reducing the communication required per multiplication gate.
        \item Proposed a dynamic segment division protocol that improves the communication complexity under best case (when every party acts honestly).
        \item Reduced the number of broadcasts required when localizing a malicious party.
    \end{listed}}
    \resumeItem{Private Storage and Computation on Blockchain}{
    \begin{listed}
        \item Exploring cryptographic primitives to add privacy guarantees to Blockchain protocols.
        \item Designed a new blockchain protocol that could not only allow the users to store their data privately but also do private computation over the private data.
    \end{listed}}
    \resumeItem{Non-malleable Multi-source Randomness Extractor}{
    \begin{listed}
        \item Designing the protocols for non-malleable multi-source randomness extractor against overlapping tampering which is stronger than independent tampering.
	\item Showed relations between non-malleable secret sharing scheme and non-malleable extractor against similar class of tampering functions.
    \end{listed}}

    \resumeItemListEnd

    \resumeSubheading{Stanford University}{Palo Alto, California}{Research Assistant with Professor Keith Winstein}{Jul. 2018 – Feb. 2019}

    \resumeItemListStart
    \resumeItem{Continual Learning Improves Internet Video Streaming}{
    \begin{listed}
        \item Designed and implemented a continual learning algorithm for bitrate selection in streaming video which combines deep learning algorithm with model predictive control.
        \item Built a video-streaming website for gathering real-world data and testing performance of different algorithms.
        \item Proposed a new transmission time prediction model that could make more accurate prediction than previous model.
    \end{listed}}
    \resumeItemListEnd

\end{itemize}

\nobibliography{publication}
\bibliographystyle{alpha}

\section*{Submitted/Manuscripts}
\begin{enumerate}
  \item \bibentry{communcation}
  \item \bibentry{yan2019continual}
\end{enumerate}

\section*{Honors \& Rewards}
\begin{itemize}
    \resumeSubheading{}{}{Yao Award (recognition price), Tsinghua University}{2019}
    \resumeSubheading{}{}{Academic Excellence Award, Tsinghua University}{2017,2018}
    \resumeSubheading{}{}{Fellowship of Xuetang Talents Program, Tsinghua University}{2017,2018}
    \resumeSubheading{}{}{Freshman Scholarship, Tsinghua University}{2016}
    \resumeSubheading{}{}{\textbf{Gold medal} in National Olympiad in Informatics (China)}{2015}
\end{itemize}

\section*{Additional Information}
\resumeItemListStart
    \resumeItem{Computer \& Language Skills}{
    \begin{listed}
        \item Programming Languages: C/C++, Java, Python, JavaScript, HTML, PHP
        \item Libraries \& Software: Django, InfluxDB, libscapi, Latex, Matlab
        \item Language: Chinese, English
    \end{listed}}
    \resumeItem{Hobbies \& Interests}{
    \begin{listed}
        \item Member of the institue's basketball and baseball teams.
        \item Rubic’s Cube: solve 3 by 3 within 20 seconds.
        \item Others: kating, Swimming, Billiards, Harmonic
    \end{listed}}
\resumeItemListEnd

\bigskip


\end{document}
